### 2025-05-05 Chapters/paper1.tex
changes

\begin{figure}
	\centering
	\includegraphics[width=0.4\linewidth]{"img/paper 1/EEG_Filter_chanel"}
	\caption{Filter EEG Chanels}
	\label{fig:eegfilterchanel}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.7\linewidth]{"img/paper 1/Architechture1"}
	\caption{Architecture of Machine Learning Classifiers for Sleep Stage
		Classificatio}
	\label{fig:architechture1}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{../img/paper_1/Random_forest/random_forest_confusion_matrix.png}
	\caption{Random Forest Confusion Matrix}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{../img/paper_1/Random_forest/accuracy_curve.png}
	\caption{Random Forest Accuracy Curve}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{../img/paper_1/Random_forest/loss_curve.png}
	\caption{Random Forest Loss Curve}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{../img/paper_1/Random_forest/precision_per_class.png}
	\caption{Random Forest Precision Per Class}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{../img/paper_1/Bagging_Boosting/BG_confusion_matrix.png}
	\caption{Bagging Classifier Confusion Matrix}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{../img/paper_1/Bagging_Boosting/accuracy_curve.png}
	\caption{Bagging Classifier Accuracy Curve}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{../img/paper_1/Bagging_Boosting/loss_curve.png}
	\caption{Bagging Classifier Loss Curve}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{../img/paper_1/Bagging_Boosting/precision_per_class.png}
	\caption{Bagging Classifier Precision Per Class}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{../img/paper_1/Ensemble_Learning/Ensemble_confusion_matrix.png}
	\caption{Ensemble Learning Confusion Matrix}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{../img/paper_1/Ensemble_Learning/accuracy_curve.png}
	\caption{Ensemble Learning Accuracy Curve}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{../img/paper_1/Ensemble_Learning/loss_curve.png}
	\caption{Ensemble Learning Loss Curve}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{../img/paper_1/Ensemble_Learning/precision_per_class.png}
	\caption{Ensemble Learning Precision Per Class}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{../img/paper_1/gradient_boosting/confusion_matrix.png}
	\caption{Gradient Boosting Confusion Matrix}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{../img/paper_1/gradient_boosting/accuracy_curve.png}
	\caption{Gradient Boosting Accuracy Curve}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{../img/paper_1/gradient_boosting/loss_curve.png}
	\caption{Gradient Boosting Loss Curve}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{../img/paper_1/gradient_boosting/precision_per_class.png}
	\caption{Gradient Boosting Precision Per Class}
\end{figure}

>>>>

\begin{figure}
	\centering
	\includegraphics[width=0.4\linewidth]{"./img/paper_1/EEG_Filter_chanel.png"}
	\caption{Filter EEG Chanels}
	\label{fig:eegfilterchanel}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.7\linewidth]{"img/paper_1/Architechture1"}
	\caption{Architecture of Machine Learning Classifiers for Sleep Stage
		Classificatio}
	\label{fig:architechture1}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{img/paper_1/random_forest_confusion_matrix.png}
	\caption{Random Forest Confusion Matrix}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{img/paper_1/accuracy_curve.png}
	\caption{Random Forest Accuracy Curve}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{img/paper_1/loss_curve.png}
	\caption{Random Forest Loss Curve}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{img/paper_1/precision_per_class.png}
	\caption{Random Forest Precision Per Class}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{img/paper_1/BG_confusion_matrix.png}
	\caption{Bagging Classifier Confusion Matrix}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{img/paper_1/accuracy_curve.png}
	\caption{Bagging Classifier Accuracy Curve}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{img/paper_1/loss_curve.png}
	\caption{Bagging Classifier Loss Curve}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{img/paper_1/precision_per_class.png}
	\caption{Bagging Classifier Precision Per Class}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{img/paper_1//Ensemble_confusion_matrix.png}
	\caption{Ensemble Learning Confusion Matrix}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{img/paper_1//accuracy_curve.png}
	\caption{Ensemble Learning Accuracy Curve}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{img/paper_1//loss_curve.png}
	\caption{Ensemble Learning Loss Curve}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{img/paper_1//precision_per_class.png}
	\caption{Ensemble Learning Precision Per Class}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{img/paper_1//confusion_matrix.png}
	\caption{Gradient Boosting Confusion Matrix}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{img/paper_1//accuracy_curve.png}
	\caption{Gradient Boosting Accuracy Curve}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{img/paper_1//loss_curve.png}
	\caption{Gradient Boosting Loss Curve}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{img/paper_1//precision_per_class.png}
	\caption{Gradient Boosting Precision Per Class}
\end{figure}
